\normalfont{A bird's-eye view on the habitability of exoplanets via statistical learning techniques}

### 2020-09-23 Manuscript/Manuscript.tex
PUB

\documentclass[
12pt, % Main document font size
a4paper, % Paper type, use 'letterpaper' for US Letter paper
oneside, % One page layout (no page indentation)
%twoside, % Two page layout (page indentation for binding and different headers)
headinclude,footinclude, % Extra spacing for the header and footer
BCOR5mm, % Binding correction
]{scrartcl}
\usepackage[english]{babel}
\usepackage{url}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}
\usepackage{epigraph}
\usepackage{mathcomp}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{url}
\usepackage{sectsty}
\usepackage[dvipsnames,table,xcdraw,svgnames]{xcolor}
\usepackage{listings}
\usepackage{url}
\lstset{language=R,
    basicstyle=\small\ttfamily,
    stringstyle=\color{DarkGreen},
    otherkeywords={0,1,2,3,4,5,6,7,8,9},
    morekeywords={TRUE,FALSE},
    deletekeywords={data,frame,length,as,character},
    keywordstyle=\color{blue},
    commentstyle=\color{DarkGreen},
}

@@

@@

We are interested in to rocky planets \footnote{In principle also moons have to be considered, however for sake of simplicity here we take into account only planets}, so gaseous ones such as Jupiter or Saturn have to be considered not habitable (see Fig. \ref{exoplanet_populations} and \ref{PT_Confirmed}); second, as requested by all form of life in the Earth, an habitable planet requires that liquid water can be present \cite{seager2013exoplanet,mckay2014requirements,rothschild2001life} \footnote{Astrobiologist scholars also proposed that other form of life can come up without liquid water (see for instance \cite{rahm2016polymorphism}) however, for simplicity, here only planets that allows liquid water are considered habitable}. This feature is given, at first glance, by the radiation intensity $I$ that is bounded to the power radiation ($P$) produced by the star that host the planet and the respective distance $r$. Indeed by approximating a star as a point or a perfect sphere, a radiation with a spherical symmetry is produced; thus the integral that gives the power produced $P$: 

@@

>>>>

\documentclass[
12pt, % Main document font size
a4paper, % Paper type, use 'letterpaper' for US Letter paper
oneside, % One page layout (no page indentation)
%twoside, % Two page layout (page indentation for binding and different headers)
headinclude,footinclude, % Extra spacing for the header and footer
BCOR5mm, % Binding correction
]{scrartcl}
\usepackage[english]{babel}
\usepackage{url}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{float}
\usepackage{titlepic}
\usepackage{epigraph}
\usepackage{mathcomp}
\usepackage{textcomp}
\usepackage{amsmath}
\usepackage{url}
\usepackage{sectsty}
\usepackage[dvipsnames,table,xcdraw,svgnames]{xcolor}
\usepackage{listings}
\usepackage{url}
\lstset{language=R,
    basicstyle=\small\ttfamily,
    stringstyle=\color{DarkGreen},
    otherkeywords={0,1,2,3,4,5,6,7,8,9},
    morekeywords={TRUE,FALSE},
    deletekeywords={data,frame,length,as,character},
    keywordstyle=\color{blue},
    commentstyle=\color{DarkGreen},
}

@@

%\titlepic{\includegraphics[width=\textwidth]{Pic/Triple-star_sunset.jpg}}

@@

Only rocky planets are considered habitable \footnote{In principle also moons have to be considered, however for sake of simplicity here we take into account only planets}, so gaseous ones such as Jupiter or Saturn have to be considered not habitable (see Fig. \ref{exoplanet_populations} and \ref{PT_Confirmed}); second, as requested by all form of life in the Earth, an habitable planet requires that liquid water can be present \cite{seager2013exoplanet,mckay2014requirements,rothschild2001life} \footnote{Astrobiologist scholars also proposed that other form of life can come up without liquid water (see for instance \cite{rahm2016polymorphism}) however, for simplicity, here only planets that allows liquid water are considered habitable}. This feature is given, at first glance, by the radiation intensity $I$ that is bounded to the power radiation ($P$) produced by the star that host the planet and the respective distance $r$. Indeed by approximating a star as a point or a perfect sphere, a radiation with a spherical symmetry is produced; thus the integral that gives the power produced $P$: 

@@

\section{Data Description}

The planet dataset was taken from the \textit{Planetary Habitability Laboratory @ UPR Arecibo} \cite{planet_dataset} website. Since the habitable planets, considering also the optimistic region, were almost 50 out of 3500, a reduction of the non-habitable planets was considered in order to make the habitable planets a significant portion of the overall set. As reported in table ***, among the different features that was provided by PHL, a restricted set was considered: such operation was performed in order to avoid features whose causal effect on the habitability (where it was present) do not require very complex models.

\section{Theoretical Background}

\section{Results and discussion}

\section{Conclusions}
